Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-12-28 cogsci/cogsci.tex
new modif on manuscript

\usepackage[subtle]{savetrees}
\usepackage{tipa}

@@

Over the first year of life, children become sensitive to the phonetic
variations that are used to distinguish meanings in their native
language (Werker and Tees, 1984). One could imagine that these
perceptual skills would be automatically applied to the task of word
learning. However, developmental data show that 14 m.o children find it
challenging to associate minimally different (but perceptually
discriminated) sounds such as ``bin'' and ``din'' to different objects
(Stager \& Werker, 1997).

Several factors can explain this pattern of results. For example it is
possible that the task of meaning learning increases cognitive demands
on children (compared to a simple perceptual descrimination). In
particular, it requires paying attention to both the sounds and the
corresponding objects, which may hinder precise encoding in memory of
some phonetic details (Stager a\& Werker, 1997). Additional difficulty
might arise from ambiguous phonological boundaries at this stage of
development (e.g., Rost \& McMurray, 2009), or from uncertainty about
the referential status of the novel word (Fennell \& Waxman, 2009).

Regardless of the exact explanation, it is generally accepted that by
around 17 m.o, chidlren succeed under the same circumstances (Werker et
al. 2002). What could be the mechanism of development? Swingley
contrasted a binary-discontinuous scenario to a probabilstic-continuous
one. On the discontinuous account, younger children learn a single,
underspecified representation of similar words (e.g., ``bin''/``din'').
Development occurs when children specify this intial coarse
reprepsentation and learn two distinct catgories. On the continuous
account, distinct represetations are successfully learned from the
start, but these representations are encoded with higher uncertainty in
youger children, leading to apparent failure in relatively demanding
tasks.

Experimental evidence suggest a probabilsitic-continuous, rather than a
stage-like develomental scenario. On the one hand, 14-month-olds who
typically fail in the original task succeed when learning is probed
using a testing method with lower memory demands (Yoshida et al. 1009),
and when uncertainty in the emerging representations is mitigated using
disambiguating contextual cues (Thiessen, 2007; Dautriche et al., 2016).
On the other hand, adults show patterns of learning similar to those
shown by 14-month-olds when the task is more challenging and when
similarity between words increases (Pajak et al., 2016; White et al.,
2013).

Following this experimental studies, the purpose of the current work is
to propose a precise probabilsitc model of the Stager and Werker's task,
and to explore the extent to which such a model could provide a unified
accounts for several documented (as well as new) patterns of learning
and development. We first present the model and explain how it can be
used to make precise predictions of the target behavioral responses.
Second, using new data collected from both preschool children and
adults, we show how the probabilistic strucure of the model can explain
behavioral patterns both within the same age and across development.

{\centering \includegraphics{figs/growth-1}

\caption{\label{fig:growth}Illustration of the growth scenarios. Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.  }\label{fig:growth}
\end{figure}
\end{CodeChunk}

@@

We model a variant of the task used in Yoshida et al. 2009. In this
task, particiants are first exposed to the association between pairs of
nonesense words (e.g., ``lif''/``neem'') and pairs of objects. After
this exposure phase, participants perform a series of two-alternative
forced choices. In each testing trial, one of the two sounds is uttered
(e.g., ``lif'') and participants choose the corresponding object from
the two alternatives.

@@

Our model consists of a set of variables describing the general process
of spoken word recognition in a referential situation. These variables
are related in a way that refelects the simple generative scenario
represented graphically in Figure XX. When a speaker utters a sound in
the presence of an object, the observer assumes that the object \(o\)
activated the concept \(C\) in the speaker's mind. The concept prompted
the cooresponding label \(L\). Finally, the label was physically
instantiated by the sound \(s\).

@@

Because of the noisy nature of the representations, the observer can
only determine the hidden variables (i.e., the concept \(C\) and the
label \(L\)) in a probabilistic fashion. For simplicity, we assume that
the probability of membership of objects and sounds to concepts and
labels, respectivel, are normally distributed:

\[ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) \]
\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \] We assume there to be
one-to-one mappings between concepts and labels, and that observers have
successfully learned these mappings during the exposure phase: \[
P(L_i|C_j) = 
\begin{cases}
  1 & \text{if  }  i=j \\  
  0  & \text{if  }  i\neq j 
\end{cases}
\] \#\# Predictions

During the testing phase (see Figure 1), participants are presented with
one target sound \(s_T \in\{s_1, s_2\}\) and two possible objects
\(o_1\) and \(o_2\). In order to make a choice, we determine which
object is more probable under the lable \(s_T\), in other words, we
compare the the probabilities \(P(o_1|s_T)\) and \(P(o_2|s_T)\). The
values of these probabilities can be computed by summing over all
possible labels:
\[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
The joint probability \(P(o, C, L, s)\) is obtained by factoring the
bayesian network in Figure 2: \[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \]
which could be tansformed using Bayes rule into:

\[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) \] Finally, assuming that the
concept prior is a uniform ditribution, we obtain the following
expression, where all conditional dependencies have been defined in the
previous secton.

From the general expression (1) we were able to derive the exact
analytical expression of the probability of correct responses in the
testing phase of our simplified experimenal setting (Figure 1).

We simulate the values of this probability as a function of the
perceptual distance between the sounds \(\Delta s\), using the two
remining parameters of the model: the visual distance between the
semantic referents \(\Delta o\) and the values of the standard deviation
of the dsitributions \(p(s| L)\) and \(p(o | C)\) (which, in this
simulation, have similar values, i.e.,
\(\sigma =\sigma_C \approx \sigma_L\)). The simulations are shown in
Figure 3.

@@

\caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits.}\label{fig:simulation}
\end{figure*}
\end{CodeChunk}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\item
  For fixed values of \(\Delta o\) and \(\sigma\), the probability of
  accurate responses increases as a function of \(\Delta s\). This
  pattern accounts for the fact that similar sounds are generally more
  challenging to learn than different sounds for both chidlren (Stager
  and Werker, 1997) and adults (Pajak et al. 2016).
\item
  For fixed values of \(\Delta s\) and \(\Delta o\), accuracy increases
  when the noise characterized with \(\sigma\) decreases. This fact may
  explain development, i.e., youger children have noisier
  representations (Swingley, 2007; Yoshida et al. 2009), which lead to
  lower word recognition accuracy, especially for similar sounding
  words.
\item
  For fixed values of \(\Delta s\) and \(\sigma\), accuracy increases
  when the visual distance between the semantic referents \(\Delta o\)
  increases. This is a new predcition that our model makes. Previous
  work studied the effect of several bottom-up and top-down properties
  in disambiguating similar sounding words (see introduction), But no
  previous study tested the effect of the visual distance between the
  semantic referents.
\end{enumerate}

To sum, we introduced a model that accounts for some qualitative
patterns observed in previous studies, and makes new predictions. In the
experiment below, we test whether the model makes accurate
\emph{quantitative} predictions by fitting it to new experimental data
collected from preschool chidlren and adults.

@@

\caption{\label{fig:illus}Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicates fixed model parameters.}\label{fig:illus}
\end{figure}
\end{CodeChunk}

@@

The sound stimuli were generated using the MBROLA Speech Synthesizer
(Dutoit et al., 1996). We generated three kinds of sound pairs which
varied in their degree of similarity to English speakers: 1)
``different'': ``lif''/``neem'' and ``zem''/``doof'', 2)
``intermediate'': ``aka''/``ama'' and ``ada''/``aba'', and 3)
``similar'' non-English minimal pairs: ``ada''/``a\textipa{d\super h}a''
(in hindi) and ``a\textipa{Q}a''/``a\textipa{\textcrh}a'' (in arabic).

@@

In a separate survey, \(N=20\) participants recruited on Amazon
Mechanical Turk evaluated the similarity of each sound and objcet pair
on a 7-point scale. We used the average ratings across participants as
qunatitaive measures of sound pairs' distance (\(\Delta s\)) and object
pairs' distance (\(\Delta o\)).

@@

\caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits.}\label{fig:all_data}
\end{figure*}
\end{CodeChunk}

@@

First we analyzed the experimental results shown in Figure (XX, left),
using a mixed-effects logistic regression with sound and object
distances as fixed effects, and with a maximal random effects strcuture
(Barr et al. 2013). Results are shown in Table XX. We found a main
effect of sound distance on the accuray of learning in both children and
adults, thus replicating previous findings. We also found a main effect
of object distance, thus confirming the new hypothesis derived from our
model.

@@

@@

>>>>

\usepackage{tipa}

@@

Over the first year of life, children become sensitive to the phonetic
variations that are used to distinguish meanings in their native
language (Werker \& Tees, 1984). One could imagine that these perceptual
skills would be automatically applied to the task of word learning.
However, developmental data show that 14 m.o children find it
challenging to associate minimally different (but perceptually
discriminated) sounds such as ``bin'' and ``din'' to different objects
(Stager \& Werker, 1997).

Several factors can explain this finding. For example it is possible
that the task of meaning learning increases cognitive demands on
children (compared to a simple perceptual descrimination). In
particular, it requires paying attention to both the sounds and the
corresponding objects, which may hinder precise encoding in memory of
some phonetic details (Hofer \& Levy, 2017; Stager \& Werker, 1997).
Additional difficulty might arise from ambiguous phonological boundaries
at this stage of development (e.g., Rost \& McMurray, 2009), or from
uncertainty about the referential status of the novel word (Fennell \&
Waxman, 2010).

Regardless of the exact explanation, it is generally accepted that by
around 17 m.o, chidlren succeed under the same circumstances (Werker,
Fennell, Corcoran, \& Stager, 2002). What could be the mechanism of
development? On one possible account, learning is stage-like: younger
children learn a single, underspecified representation of similar words
(e.g., ``bin''/``din''). Development occurs when children specify this
intial coarse reprepsentation and learn two distinct catgories. On an
other account, learning is continuous: distinct represetations are
learned even by younger children, but these representations are encoded
with higher uncertainty in youger children, leading to apparent failure
in relatively demanding tasks. Development is a continuous process
whereby the intinial noisy representations become more precise (see
also, Swingley, 2007).

Experimental evidence suggest a probabilsitic/continuous, rather than a
binary/discontinuous develomental scenario. On the one hand,
14-month-olds who typically fail in the original task succeed both when
an easier testing method is used (Yoshida, Fennell, Swingley, \& Werker,
2009), and when uncertainty is mitigated via disambiguating cues
(Dautriche, Swingley, \& Christophe, 2015; Thiessen, 2007). On the other
hand, adults show patterns of learning similar to those shown by
14-month-olds when the task is more challenging and when similarity
between words increases (Pajak, Creel, \& Levy, 2016; White, Yee,
Blumstein, \& Morgan, 2013).

In the light of these evidence, the purpose of the current work is to
propose a precise probabilsitc model of the Stager and Werker's task
where developmment is understood to proceed in a continuous fashion
across the lifespan. We use this model to both provide a unifying
account for documented experimental findings, and to make new
predicitions that have not been tested before. Using new data collected
from both preschool children and adults, we show that the model can
explain various patterns of learning both within the same age and across
development.

@@

We model the word learning task introduced by Stager \& Werker (1997),
and a testing method similar to the one used by Yoshida et al. (2009).
In this task, particiants are first exposed to the association between
pairs of nonesense words (e.g., ``lif''/``neem'') and pairs of objects.
After this exposure phase, participants perform a series of
two-alternative forced choices. In each testing trial, one of the two
sounds is uttered (e.g., ``lif'') and participants choose the
corresponding object from the two alternatives. An overview of the task
is shown in Figure~@ref(fig:task).

\begin{CodeChunk}
\begin{figure}[t]

{\centering \includegraphics{figs/task-1}

\caption{\label{fig:task}An overview of the task used in this study.}\label{fig:task}
\end{figure}
\end{CodeChunk}

@@

Our model consists of a set of variables describing the general process
of spoken word recognition in a referential situation. These variables
are related in a way that refelects the simple generative scenario
represented graphically in Figure~@ref(fig:model). When a speaker utters
a sound in the presence of an object, the observer assumes that the
object \(o\) activated the concept \(C\) in the speaker's mind. The
concept prompted the cooresponding label \(L\). Finally, the label was
physically instantiated by the sound \(s\).

Because of the noisy nature of the representations, the observer can
only determine the hidden variables (i.e., the concept \(C\) and the
label \(L\)) in a probabilistic fashion. For simplicity, we assume that
the probability of membership of objects and sounds to concepts and
labels, respectively, are normally distributed:

\[ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) \]
\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \] We assume there to be
one-to-one mappings between concepts and labels, and that observers have
successfully learned these mappings during the exposure phase: \[
P(L_i|C_j) = 
\begin{cases}
  1 & \text{if  }  i=j \\  
  0  & \text{if  }  i\neq j 
\end{cases}
\]

\subsection{Simulations}\label{simulations}

During the testing phase, participants are presented with one target
sound \(s_T \in\{s_1, s_2\}\) and the two objects \(o_1\) and \(o_2\)
presented during the learning phase. In order to make a choice, we
determine which object is more probable under the target sound \(s_T\),
in other words, we compare the the probabilities \(P(o_1|s_T)\) and
\(P(o_2|s_T)\). The values of these probabilities can be computed by
summing over all possible concepts and labels:
\[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
The joint probability \(P(o, C, L, s)\) is obtained by factoring the
bayesian network in Figure 2: \[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \]
which could be tansformed using Bayes rule into:

\[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) \] Finally, assuming that the
concept prior probability is uniformly ditributed, we obtain the
following expression, where all conditional dependencies have been
defined in the previous sub-section.

From the general expression (1) we derive the exact analytical formula
which expresses the probability of accurate responses in the testing
phase (Figure 1).

\begin{CodeChunk}
\begin{figure}[h]

@@

We provide an intuitive illustration of how this probabilistic account
explain patterns of learning and development in Figure XX. Low accuracy
in word learning occurs when the perceptual distance between the labels
is small relative to the uncertainty with wich these labels are encoded.
For example, in Stager and Werker's orginal experiment, children are
supposed to associate lable 1 (``bih'') and label 2 (``dih'') with
object 1 and object 2, respectively. Though children could learn that
the label ``bih'' is a better match to object 1 than ``dih'', they could
still judge the sound ``dih'' as a plausible instance of the lable
``bih'', thanks to the relatively large variance/tolerance of the
encoding.

Accuracy is high when the perceptual distance between the labels is
large relative to the uncertainty of their encoding. Thus, improvement
can occur in the same developmental stage if the perceptual distance of
the labels is enhanced either through using different-sounding labels
(e.g., ``lif'' vs. ``neem'' instead of ``bih'' and ``dih'') or through
using additional disambiguating cues (e.g., Thiessen, 2007). Accuracy
improves over development because the encoding's uncertainty itself is
reduced.

In order to have a more quantitative understanding of the mdoel, we
simulate the values of the predicted accuracy (Expression 2) as a
function of the perceptual distance between the sounds \(\Delta s\). We
used as parameters the two remaning variables, i.e., the visual distance
between the semantic referents \(\Delta o\) and the standard deviation
of the dsitributions \(p(s| L)\) and \(p(o | C)\) (which, in this
simulation, have similar values, i.e.,
\(\sigma =\sigma_C \approx \sigma_L\)). The simulations are shown in
Figure 3.

@@

\caption{\label{fig:simulation}The predicted probability of accurate responses in the task of learning two similar-sounding words, as a function the perceptual distance between the sounds. Colors indicate different values of the standard deviation which we assume is common to both the label and concept probabilistic representations. Panels represent graphs using different values of the visual distance between the objects.}\label{fig:simulation}
\end{figure*}
\end{CodeChunk}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\item
  For fixed values of \(\Delta o\) and \(\sigma\), the probability of
  accurate responses increases as a function of \(\Delta s\). This
  pattern accounts for the fact that similar sounds are generally more
  challenging to learn than different sounds for both chidlren (Stager
  \& Werker, 1997) and adults ({\textbf{???}}).
\item
  For fixed values of \(\Delta s\) and \(\Delta o\), accuracy increases
  when the representational noise (characterized with \(\sigma\))
  decreases. This fact may explain development, i.e., youger children
  have noisier representations (Swingley, 2007; Yoshida et al., 2009),
  which leads to lower word recognition accuracy, especially for similar
  sounding words.
\item
  For fixed values of \(\Delta s\) and \(\sigma\), accuracy increases
  with the visual distance between the semantic referents \(\Delta o\).
  This is a new predcition that our model makes. Previous work studied
  the effect of several bottom-up and top-down properties in
  disambiguating similar sounding words (see review in the
  introduction), But no previous study tested the effect of the visual
  distance between the semantic referents.
\end{enumerate}

To sum, we introduced a model that accounts for some qualitative
learning patterns observed in previous studies, and makes a new
prediction. In the experiment below, we test whether the model makes
accurate \emph{quantitative} predictions by fitting it to new
experimental data collected from preschool chidlren and adults.

@@

\caption{\label{fig:illus} An illustration of how a probabilsitic account (where distinct categories are encoded with different degrees of uncertainty) can explain patterns of learning and development. Accuracy experesses the extent to which a given sound instance indicates a unique category. The values vary between 0.5 (total overlap) and 1 (no overalp). Accuracy is low when the perceptual distance between labels is small relative to the category variance. Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development).}\label{fig:illus}
\end{figure}
\end{CodeChunk}

@@

The sound stimuli were generated using the MBROLA Speech Synthesizer
(Dutoit, Pagel, Pierret, Bataille, \& Van der Vrecken, 1996). We
generated three kinds of sound pairs which varied in their degree of
similarity to English speakers: 1) ``different'': ``lif''/``neem'' and
``zem''/``doof'', 2) ``intermediate'': ``aka''/``ama'' and
``ada''/``aba'', and 3) ``similar'' non-English minimal pairs:
``ada''/``a\textipa{d\super h}a'' (in hindi) and
``a\textipa{Q}a''/``a\textipa{\textcrh}a'' (in arabic).

@@

In a separate survey, \(N=20\) participants recruited on Amazon
Mechanical Turk evaluated the similarity of each sound and objcet pair
on a 7-point scale. We computed averge ratings across partcipants, and
we normalized the data so that the values vary between 0 to 1. Results
are shown in Figure XX, for each stimuli group. This data will be used
in the models as the perceptual distance of sound pairs (\(\Delta s\))
and object pairs (\(\Delta o\)).

\begin{CodeChunk}
\begin{figure}[h]

{\centering \includegraphics{figs/stim-1}

\caption{\label{fig:stim}Normalized distances for both sound and object pairs used in this study.}\label{fig:stim}
\end{figure}
\end{CodeChunk}

@@

\caption{\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs. Adults). Experimental results are shown on the left. Predictions from Model 1 (one free parameter) and Model 2 (two free parameters) are shown in the middle and on the right, respectively.}\label{fig:all_data}
\end{figure*}
\end{CodeChunk}

@@

First we analyzed the experimental results shown in Figure (XX, left),
using a mixed-effects logistic regression with sound and object
distances as fixed effects, and with a maximal random effects strcuture
(Barr, Levy, Scheepers, \& Tily, 2013). Results are shown in Table XX.
We found a main effect of sound distance on the accuray of learning in
both children and adults, thus replicating previous findings. We also
found a main effect of object distance, thus confirming the new
prediction of our model.

@@

Figures XX (middle and right graphs) show the predictions of the models.
Both model 1 and model 2 fit reseanaby well the the experimental data in
both children and adults. They both correcly predict the relative
recognition accuacy accross conditions: the pair of words that differ on
both the object and sound levels were the easiest to learn, followed by
the pairs of words that differ on only one level, then the pair of words
that are similar on both levels.

For Model 1, we obtained a noise parameter of \(\sigma =\) 0.63 {[}0.53,
0.73{]} for preschoolers, and \(\sigma =\) 0.16 {[}0.12, 0.19{]} for
adults. It explained the majority of the variance (\(R^2=\) 0.94). For
model 2, children had a sound specific noise of \(\sigma_S =\) 0.9
{[}0.68, 1.11{]}, and a concept specific noise of \(\sigma_C =\) 0.29
{[}0.1, 0.49{]}. Adults had a concept specific noise of \(\sigma_C =\)
0.14 {[}0.05, 0.23{]}, and a sound specific noise of \(\sigma_S =\) 0.16
{[}0.05, 0.28{]}. The model explain almost all the variance (\(R^2=\)
0.96).

\section{General Discussion}\label{general-discussion}

@@

\hypertarget{refs}{}
\hypertarget{ref-barr2013}{}
Barr, D., Levy, R., Scheepers, C., \& Tily, H. (2013). Random effects
structure for confirmatory hypothesis testing: Keep it maximal.
\emph{Journal of Memory and Language}, \emph{68}(3).

\hypertarget{ref-dautriche2015}{}
Dautriche, I., Swingley, D., \& Christophe, A. (2015). Learning novel
phonological neighbors: Syntactic category matters. \emph{Cognition},
\emph{143}.

\hypertarget{ref-dutoit1996}{}
Dutoit, T., Pagel, V., Pierret, N., Bataille, F., \& Van der Vrecken, O.
(1996). The mbrola project: Towards a set of high quality speech
synthesizers free of use for non commercial purposes. In
\emph{Proceedings of ICSLP} (Vol. 3). IEEE.

\hypertarget{ref-fennell2010}{}
Fennell, C., \& Waxman, S. (2010). What paradox? Referential cues allow
for infant use of phonetic detail in word learning. \emph{Child
Development}, \emph{81}.

\hypertarget{ref-hofer2017}{}
Hofer, M., \& Levy, R. (2017). Modeling Sources of Uncertainty in Spoken
Word Learning. In \emph{Proceedings of the 39th Annual Meeting of the
Cognitive Science Society}.

\hypertarget{ref-pajak2016}{}
Pajak, B., Creel, S., \& Levy, R. (2016). Difficulty in learning
similar-sounding words: A developmental stage or a general property of
learning? \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{42}(9).

\hypertarget{ref-rost2009}{}
Rost, G. C., \& McMurray, B. (2009). Speaker variability augments
phonological processing in early word learning. \emph{Developmental
Science}, \emph{12}.

\hypertarget{ref-stager1997}{}
Stager, C., \& Werker, J. (1997). Infants listen for more phonetic
detail in speech perception than in word-learning tasks. \emph{Nature},
\emph{388}(6640).

\hypertarget{ref-swingley2007}{}
Swingley, D. (2007). Lexical exposure and word-form encoding in
1.5-year-olds. \emph{Developmental Psychology}, \emph{43}(2).

\hypertarget{ref-thiessen2007}{}
Thiessen, E. (2007). The effect of distributional information on
children's use of phonemic contrasts. \emph{Journal of Memory and
Language}, \emph{56}.

\hypertarget{ref-werker1984}{}
Werker, J., \& Tees, R. (1984). Cross-language speech perception:
Evidence for perceptual reorganization during the first year of life.
\emph{Infant Behavior and Development}, \emph{7}.

\hypertarget{ref-werker2002}{}
Werker, J., Fennell, C., Corcoran, K., \& Stager, C. (2002). Infants'
ability to learn phonetically similar words: Effects of age and
vocabulary size. \emph{Infancy}, \emph{3}.

\hypertarget{ref-white2013}{}
White, K., Yee, E., Blumstein, S., \& Morgan, J. (2013). Adults show
less sensitivity to phonetic detail in unfamiliar words, too.
\emph{Journal of Memory and Language}, \emph{68}(4).

\hypertarget{ref-yoshida2009}{}
Yoshida, K., Fennell, C., Swingley, D., \& Werker, J. (2009).
14-month-olds learn similar-sounding words. \emph{Developmental
Science}, \emph{12}.
